\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{

  \item[$\circ$]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[rightmargin=1.9cm]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Owen Oertell} \\ \vspace{6pt}
  \small \href{https://owenoertell.com}{\underline{owenoertell.com}} $|$ \href{mailto:ojo2@cornell.edu}{\underline{ojo2@cornell.edu}} $|$
  \href{https://linkedin.com/in/owen-oertell}{\underline{linkedin.com/in/owen-oertell}} $|$
  \href{https://github.com/owen-oertell}{\underline{github.com/owen-oertell}} $|$ \href{tel:1-404-491-4223}{\underline{+1 (404) 491-4223}} $|$ US Citizen
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Cornell University}{Ithaca, NY}
{B.S. in Computer Science, Electrical Computer Engineering; Minor in Mathematics.}{Expected Graduation: May 2025}
\resumeItemListStart
\resumeItem{\textbf{Relevant Coursework}: Introduction to Algorithms, Object Oriented Programming \& Data Structures, Advanced Linear Algebra}
\resumeItemListEnd
\resumeSubheading
{Georgia Institute of Technology}{Atlanta, GA}
{Full Time Dual Enrollment; GPA: 4.0/4.0.}{Aug 2021 - May 2022}
\resumeItemListStart
\resumeItem{\textbf{Relevant Coursework}: Linear Algebra, Multivariable Calculus, Differential Equations, Discrete Mathematics, \textbf{Graduate Level} Computational Foundations of Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Lab Researcher}{May 2020 – Present}
{Dickson Lab, Georgia Institute of Technology $\cdot$ Part-Time}{Atlanta, GA}
\resumeItemListStart
\resumeItem{Adapted C code from bacterial genome to the human genome for novel copy number variation detection algorithm.}
\vspace{-10pt}
\resumeItem{Reduced memory consumption by 300GB while maintaining speed via parallelization and low-level C programming.}
\vspace{-10pt}
\resumeItem{Assisted in development of efficient blood assay technique for bacterial infection identification.}
\resumeItem{Increased data gathering speed by 4x by writing code to use multiple cameras in parallel with single camera port.}
\vspace{-11pt}
\resumeItem{Co-authored low budget blood assay technique paper publication submission in process.}
\resumeItem{\textbf{Utilities}: C (Serial and Parallelized), OpenMP, OpenACC, Makefiles, OpenCV, Linux, Python, Valgrind}
\resumeItemListEnd

\resumeSubheading
{Head of Engineering, Secretary on Board of Directors}{April 2020 – July 2022}
{Y STEM and Chess Inc 501(c)(3) $\cdot$ Internship}{Boise, ID}
\resumeItemListStart
\resumeItem{Managed 30 undergraduate and professional SWEs.}
\resumeItem{Led development of website: \href{https://ystemandchess.com}{\underline{YStemAndChess.com}} to provide free mentoring of underprivileged children from around the world. Helped expand Y STEM and Chess to tutor more than 800 children.}
\resumeItem{Interviewed and hired interns and full time developers.}
\resumeItem{Engineered and implemented scalable microservice architecture designs to minimize cost.}
\resumeItem{Led development of real-time chess pairing and mentoring system.}
\resumeItem{Implemented recording storage system allowing parents and students to review lessons.}
\resumeItem{\textbf{Utilities}: Node.js, PHP, AWS, Angular.js, MongoDB, Docker, Kubernetes}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{PrepByAI.com (Co-Founder)}}{June 2021 – May 2022 }
\resumeItemListStart
\resumeItem{Led development of website: \href{https://PrepByAI.com}{\underline{PrepByAI.com}}, a free ACT preparation site.}
\resumeItem{Built machine learning model to identify needs and suggest questions to improve performance using term frequency–inverse document frequency and k-means clustering.}
\resumeItem{Over 500 regular users and 9,000+ questions answered to date.}
\resumeItem{\textbf{Utilities}: Flask, PostgreSQL, TensorFlow, React.js, JavaScript, Python}
\resumeItemListEnd

\resumeProjectHeading{\textbf{DataManager (Large Scale Image Anomaly Detection)}} {March 2021}
\resumeItemListStart
\resumeItem{Created efficient variational audoencoder to detect anomalies in large image datasets.}
\resumeItem{Added Electron.js frontend to create desktop application to apply, detect and confirm or remove anomalous images before deep learning tasks.}
\resumeItem{\textbf{Utilities}: TensorFlow, React.js, Electron.js, JavaScript, Python}
\resumeItemListEnd


\resumeSubHeadingListEnd

%----------AWARDS----------------------
\section{Awards}
\resumeItemListStart
\resumeItem{Salutatorian of Chamblee High School (Magnet Program)}
\vspace{-5pt}
\resumeItem{$2$nd at Technology Student Assocation National Competition in software development among $500+$ submissions for DataManager project.}
\vspace{-5pt}
\resumeItem{Georgia Science and Engineering Fair Award for \textit{Novel Application of Document Distance for CNV Detection}.}
\vspace{-5pt}
\resumeItem{National Merit Scholarship Recipient.}
\vspace{-5pt}
\resumeItem{Presidential Scholar Semi-finalist.}
\vspace{-5pt}
\resumeItem{Top $25$ at Technology Student Assocation National Competition in data science among $500+$ submissions for pulsar star detection deep neural network.}
\vspace{-5pt}\resumeItemListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills And Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Languages}{: C (OpenACC, OpenMP), C++, C\#, Java, JavaScript, Python, Ruby, HTML/CSS, SQL}\\
                \textbf{Frameworks}{: React.js, Angular.js, Electron.js, Node.js, Express.js, .NET core} \\
                \textbf{Developer Tools}{: Jupyter Notebooks, Git, Docker, Kubernetes, VS Code, Amazon AWS, VIM, Makefiles} \\
                \textbf{Libraries}{: Pandas, OpenCV, TensorFlow, Pillow, Numpy, Matplotlib, Valgrind}\\
                \textbf{Databases}{: PostgreSQL, MongoDB}\\
                \textbf{Interests}{: Mathematics (Pure and Applied), Thoretical Machine Learning, Go (board game), Magic: The Gathering, Golf\\
                }}}
\end{itemize}
%-------------------------------------------
\end{document}