\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[margin = 1in]{geometry}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{graphicx}

%--------------UNDERLINING---------------

\usepackage{contour}
\usepackage{ulem}

\renewcommand{\ULdepth}{3.8pt}
\contourlength{0.8pt}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

%----------------------------------------

\graphicspath{ {./Images/} }

%----------FONT OPTIONS----------
\usepackage{fontspec}
\usepackage{fontawesome5}

\setmainfont{XCharter}

\newfontfamily{\basictitle}{basictitlefont}[
Path = Fonts/,
Extension = .ttf,
UprightFont = basictitlefont
]
% to use:
% {\basictitle This text uses the basictitle font}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\iffalse
% \iftrue
\addtolength{\oddsidemargin}{0.3in}
\addtolength{\marginparsep}{0.3in}
\addtolength{\evensidemargin}{0.3in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{0.3in}
\addtolength{\textheight}{0.3in}
\fi

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    {\color{gray}\titlerule} \vspace{-5pt}
    \vspace{8pt}\scshape\raggedright\normalfont
}{}{0pt}{}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------


\begin{document}


%----------HEADING----------

{\basictitle \Huge \textbf{Owen Oertell}}
\vspace{10pt}
% ----- TOGGLE FOR PHOTO ----
% \vspace{10pt}
\small {

  \href{mailto:owen@oertell.net}{
    \faEnvelope
    \thinspace \thinspace
    \myuline{owen@oertell.net}} $|$
  \href{https://www.linkedin.com/in/owen-oertell/}{
    \faLinkedin
    \thinspace \thinspace
    \myuline{owen-oertell}} $|$
  \href{https://github.com/owen-oertell}{
    \faGithub
    \thinspace \thinspace
    \myuline{Owen-Oertell}} $|$
  \faPhone
  \thinspace \thinspace
  404 491 4223 $|$
  \href{https://owenoertell.com}{
    \faGlobe
    \thinspace \thinspace
    \myuline{owenoertell.com}}
}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Chamblee Charter High School}{Atlanta, GA}
{High School Diploma, Class of 2022}{August 2018 -- Present}
\resumeItemListStart

\resumeItem{4.0 UW / 4.57 W}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Head of Engineering}{April 2020 -- Present}
{Y Stem and Chess Inc. 501(c)(3)}{Atlanta, Georgia}
\resumeItemListStart
\resumeItem{Led development of website: \myuline{\href{https://ystemandchess.com}{ystemandchess.com}}}
\resumeItem{Manage 30 undergraduate and professional SWEs}
\resumeItem{Engineered scalable architecture designs to minimize cost}
\resumeItem{Built real-time chess paring and mentor system}
\resumeItem{Allowed for free mentoring of underprivileged children}
\resumeItem{\textbf{Utilities:} Node.js, PHP, Angular.js, MonogDB, Docker}
\resumeItemListEnd

\resumeSubheading
{Lab Member}{May 2020 -- Present}
{Dickson Lab, Georgia Institute of Technology}{Atlanta, Georgia}
\resumeItemListStart
\resumeItem{Adapting C code from bacterial genome to human genome}
\resumeItem{Reduced memory consumption by 300GB}
\resumeItem{\textbf{Utilities:} C, Makefiles}
\resumeItemListEnd

\resumeSubheading
{Co-Founder}{June 2021 -- Present}
{PrepByAI}{Atlanta, Georgia}
\resumeItemListStart
\resumeItem{Led development of website: \myuline{\href{https://prepbyai.com}{prepbyai.com}}}
\resumeItem{Built machine learning model to improve ACT study efficiency. }
\resumeItem{Over 150 regular users and 3,000 questions answered.}
\resumeItem{\textbf{Utilities:} React, Python, Flask, Tensorflow}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ECs-----------
\section{Extracurriculars}
\resumeSubHeadingListStart

\resumeSubheading
{President}{2020 - Present}
{CCHS Technology Student Association}{}
\resumeItemListStart
\resumeItem{Lead community \& internal meetings for the organization}
\resumeItem{Grew membership by >50\%}
\resumeItem{Chapter entries placed nationally for first time since 2015}
\resumeItemListEnd

\resumeSubheading
{Secretary}{October 2020 - Present}
{YStem and Chess Inc. Board of Directors}{}
\resumeItemListStart
\resumeItem{Provide technical and financial advice to the board.}
\resumeItem{Report findings of the board to engineering division.}
\resumeItemListEnd

\resumeSubheading
{Captain}{August 2018 -- Present}
{Vex Robotics Team 1275E and 1275A}{}
\resumeItemListStart
\resumeItem{Lead programming for of robot for autonomous and diver control period.}
\resumeItem{Top 150 in world robotics skills ranking}
\resumeItemListEnd


\resumeSubheading
{Treasurer}{April 2020 -- Present}
{National Honor Society}{}
\resumeItemListStart
\resumeItem{Manage member dues and orchestrate induction ceremony.}
\resumeItemListEnd

\resumeSubheading
{Hebrew School Teacher's Assistant}{August 2017 -- Present}
{Temple Sinai}{}
\resumeItemListStart
\resumeItem{Teach students Hebrew and Jewish values.}
\resumeItemListEnd

\resumeSubheading
{Philosophy Group Leader}{August 2017 -- Present}
{Temple Sinai}{}
\resumeItemListStart
\resumeItem{Taught lessons about the intersection between the Talmud and modern philisophical topics in 6 week .}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Awards}
\resumeSubHeadingListStart
\resumeSubheading{2nd Place Nationally for Software Development}{2021}
{Technology Student Association National Competition. > 500 entries.}{}
\resumeSubheading{Top 25 Nationally for Data Science and Analytics}{2021}
{Technology Student Association National Competition. >500 entries.}{}
\resumeSubheading{USACO Silver Division}{2020}{USA Computing Olympiad}{}
\resumeSubheading{Georgia Certificate of Merit}{2021}{Top 5\% of Junior Class}{}
\resumeSubheading{Keynote Lecturer}{2021}{Gave lecture, \myuline{\href{https://github.com/Owen-Oertell/introToMLConcretePrediction/raw/main/slide.pdf}{\textbf{Introduction to Machine Learning}}}, to over 130 people}{}
\resumeSubheading{1st Place for Computer Programming}{2020}{Dekalb County Technology Fair}{}
\resumeSubheading{Chamblee High School Math Award}{2020}{Awarded for outstanding achievement and mathematical ability in sophomore class}{2 / 450 Students}
\resumeSubheading{Chamblee High School Student of Distinction}{2019}{Awarded for leadership and character out of entire freshmen class}{3 / 500 Students}
\resumeSubheading{Test Scores}{}{ACT: 36, PSAT: 1500}{}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Languages}{: Python, C/C++, SQL, MongoDB, PHP, JavaScript, Java, HTML/CSS} \\
                \textbf{Frameworks}{: Angular, React, Tensorflow} \\
                \textbf{Developer Tools}{: Jupyter Notebooks, Git, Docker, Kubernetes, VS Code, Amazon AWS} \\
                \textbf{Libraries}{: pandas, numpy, matplotlib, opencv}
          }}
\end{itemize}

%-------------------------------------------
\end{document}
